Title: Determining multi-scale controls on river temperature: a time series approach

### 2017-04-21 manuscript/vlah_chapter2_draft.tex
added draft version of manuscript

\author{Michael Vlah and Gordon Holtgrieve}
\title{Determining multi-scale controls on river temperature: a time series approach}

@@

\maketitle
\clearpage

@@

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/map/puget_sound_labeled.png}}
\textbf{Figure 1} Site locations (red points) in relation to combined Washington State Climate Divisions 3 and 4 (colored topography), the region across which climate data were aggregated. See Appendix C for site information.
\end{center}

@@

% \begin{table}
\begin{center}
\textbf{Table 1} Watershed classification scheme
\end{center}
\begin{center}
\begin{tabular}{ |c|c|c|c| }
 \hline
 Classification & Abb. & Glaciation (\%) & Mean elev. (m) \\
 \hline
 Rain-dominated & RD & $< 0.7$ & $< 600$ \\
 Rain-and-snow & RS & $< 0.7$ & $\geq 600$ \\
 Snow-dominated & SD & $\geq 0.7$ & - \\
 \hline
\end{tabular}
\end{center}
% \end{table}

@@

% \begin{figure}[h!]
\begin{center}
% \includegraphics[width=\textwidth]{figures/16_temp_all_reg.pdf}
\resizebox{\textwidth}{!}{\includegraphics{figures/12_air_water_discharge.pdf}}
% \caption{Epipolar Geometry}
% \label{fig:air_water_disch}
\end{center}
% \end{figure}

\noindent
\textbf{Figure 2} Monthly mean T\textsubscript{water} by river class, and T\textsubscript{air} and Q across classes, from 1978 to 2015. All depicted series represent discrete data. %\setlength{\parskip}{6pt}
\\[\baselineskip]

@@

% \begin{tikzpicture}
%     \draw (0, 0) node[inner sep=0] {\includegraphics[width=\textwidth]{figures/16_temp_all_reg.pdf}};
%     \draw (-4.1, -2.1) node[text width=9.5em] {\normalsize \textbf{Figure 3} Relationships between watershed elevation and climatic effects on T\textsubscript{water} \textbf{(a-c)}, and other watershed predictors and factor loadings on shared trends \textbf{(d-g)}. Points are sized by watershed area. Regression lines indicate slopes significant at $\alpha=0.05$.};
% \end{tikzpicture}
\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/19_temp_simp_reg.pdf}}
% \textbf{Figure 3} Relationships between watershed elevation and climatic effects on T\textsubscript{water} \textbf{(a-c)}, and between watershed features and factor loadings on shared trends \textbf{(d-e)}. Regression lines indicate slopes significant at $\alpha=0.1$.
\resizebox{\textwidth}{!}{\includegraphics{figures/18_PCoA.pdf}}
\end{center}
\textbf{Figure 3} (a-c) Relationships between watershed elevation and climatic effects on T\textsubscript{water}, obtained from full model fit. (d-e) Relationships between watershed features and factor loadings on shared trends, from constrained model fit. Regression lines indicate slopes significant at $\alpha=0.1$. (f) Ordination of landscape predictors by principal coordinates analysis. Length and direction of arrows are proportional to loading of landscape predictors onto each principal axis of their variation.
\\[\baselineskip]

@@

\bibliography{manuscript}
\bibliographystyle{apalike}
\clearpage

>>>>

\author{Authors: Michael Vlah* and Gordon Holtgrieve}
\title{Title: Determining multi-scale controls on river temperature: a time series approach}

@@

\maketitle
\noindent
Affiliation: School of  Aquatic and Fishery Sciences, University of Washington, Seattle, WA 98105
\\[\baselineskip]
\noindent
*Corresponding author: vlahm13@gmail.com, 412-735-3706
\clearpage

@@

@@

@@

@@

@@

\clearpage
\bibliography{manuscript}
\bibliographystyle{apalike}
\clearpage

\section*{Tables}
% \begin{table}
\begin{center}
\textbf{Table 1} Watershed classification scheme.
\end{center}
\begin{center}
\begin{tabular}{ |c|c|c|c| }
 \hline
 Classification & Abb. & Glaciation (\%) & Mean elev. (m) \\
 \hline
 Rain-dominated & RD & $< 0.7$ & $< 600$ \\
 Rain-and-snow & RS & $< 0.7$ & $\geq 600$ \\
 Snow-dominated & SD & $\geq 0.7$ & - \\
 \hline
\end{tabular}
\end{center}
% \end{table}

\section*{Figures}
\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/map/puget_sound_labeled.png}}
\textbf{Figure 1} Site locations (red points) in relation to combined Washington State Climate Divisions 3 and 4 (colored topography), the region across which climate data were aggregated. See Appendix C for site information.
\end{center}

% \begin{figure}[h!]
\begin{center}
% \includegraphics[width=\textwidth]{figures/16_temp_all_reg.pdf}
\resizebox{\textwidth}{!}{\includegraphics{figures/12_air_water_discharge.pdf}}
% \caption{Epipolar Geometry}
% \label{fig:air_water_disch}
\end{center}
% \end{figure}
\noindent
\textbf{Figure 2} Monthly mean T\textsubscript{water} by river class, and T\textsubscript{air} and Q across classes, from 1978 to 2015. All depicted series represent discrete data. %\setlength{\parskip}{6pt}
\\[\baselineskip]

% \begin{tikzpicture}
%     \draw (0, 0) node[inner sep=0] {\includegraphics[width=\textwidth]{figures/16_temp_all_reg.pdf}};
%     \draw (-4.1, -2.1) node[text width=9.5em] {\normalsize \textbf{Figure 3} Relationships between watershed elevation and climatic effects on T\textsubscript{water} \textbf{(a-c)}, and other watershed predictors and factor loadings on shared trends \textbf{(d-g)}. Points are sized by watershed area. Regression lines indicate slopes significant at $\alpha=0.05$.};
% \end{tikzpicture}
\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/19_temp_simp_reg.pdf}}
% \textbf{Figure 3} Relationships between watershed elevation and climatic effects on T\textsubscript{water} \textbf{(a-c)}, and between watershed features and factor loadings on shared trends \textbf{(d-e)}. Regression lines indicate slopes significant at $\alpha=0.1$.
\resizebox{\textwidth}{!}{\includegraphics{figures/18_PCoA.pdf}}
\end{center}
\textbf{Figure 3} (a-c) Relationships between watershed elevation and climatic effects on T\textsubscript{water}, obtained from full model fit. (d-e) Relationships between watershed features and factor loadings on shared trends, from constrained model fit. Regression lines indicate slopes significant at $\alpha=0.1$. (f) Ordination of landscape predictors by principal coordinates analysis. Length and direction of arrows are proportional to loading of landscape predictors onto each principal axis of their variation.
